Python as a machine learning language: experiences from the \textit{scikit-learn} project

### 2013-06-05 paper.tex
Intro of section 2

\begin{abstract}
The \textit{scikit-learn} project is an increasingly popular open source machine
learning library designed to be simple and efficient, accessible to non-experts,
and reusable in various contexts. In this paper, we present and discuss our
design choices for the application programming interface (API) of the project.
In particular, we describe our core \textit{estimator} interface shared by all
learning and processing units in the library and then discuss its advantages in
terms of composition and reusability. The paper also comments on implementation
details specific to the Python ecosystem and highlights obstacles faced by users
and developers of the library.
\end{abstract}

@@

>>>>

\begin{abstract}
The \textit{scikit-learn} project is an increasingly popular open source machine
learning library designed to be simple and efficient, accessible to non-experts,
and reusable in various contexts. In this paper, we present and discuss our
design choices for the application programming interface (API) of the project.
In particular, we describe the core \textit{estimator} interface shared by all
learning and processing units in the library and then discuss its advantages in
terms of composition and reusability. The paper also comments on implementation
details specific to the Python ecosystem and highlights obstacles faced by users
and developers of the library.
\end{abstract}

@@

In this section, we discuss the general principles of the application programming
interface (API) of \textit{scikit-learn}. We first specify the representation
of data and then proceed by describing the interface shared by all learning
processing units of the library. We then discuss the composition and reusability
advantages of that interface.
